Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2022-08-10 experiments/2_supplement/supplement.Rmd
add graph to supplement

>>>>

# Is it really functional diversity?

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method_ELErevision1.RDS"))

## a fudge to test a test dataset, should be removed when final dataset is available
all_stab <- all_stab %>%
  mutate(waittime = ifelse(num_strains == -1, 1e6, waittime))

which_strains <- c(-1, 9)
which_wait_time <- 1e6
figure_title <- " "

fig_div_vs_o2diff_maxtolcomp(all_stab, which_strains,
                              which_wait_time, figure_title)
```
